---
title: "MicroMove: simulating urban travel patterns from the bottom up"
author: "Robin Lovelace and Andrew Smith"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: ref.bib
---

```{r, eval=FALSE}
# Get bibliography (run once from project root)
u = "https://www.zotero.org/api/groups/418217/collections/MP7NS3SC/items/top?limit=100&format=bibtex&v=1"
b = httr::GET(url = u, httr::write_disk("ref.bib", overwrite = T))
```

The R package **synthpop** provides a set of tools for generating synthetic data, in the context of anonymisation rather than modelling [@nowok_synthpop:_2016]. ...

@kavroudakis_sms:_2015 focus on the spatial variability of individual-level dat.

## Introduction




## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

## References
